### 2014-04-16 text/Chapter02.tex
Flat coeffect systems in Chapter 03

>>>>

\section{Context oriented programming}

The importance of context-aware computations is perhaps most obvious when considering mobile
application, client/server web applications or even the internet of things. A pioneering work
in the area using functional languages has been done by Serrano \cite{app-hop-diffuse,app-hop-lang}
(which also inspired the example presented in Chapter~\ref{ch:intro}). His HOP language supports 
cross-compilation and programs execute in different contexts. However, HOP is not statically 
type checked.

In the software engineering community, a number of authors have addressed the
problem of context-aware computations. Hirschfeld et al. propose \emph{Context-Oriented Programming} 
(COP) as a methodology \cite{app-cop-method}. The COP paradigm has been later implemented by
programming language features. Costanza \cite{app-cop-contextl} develops a domain-specific LISP-like 
language ContextL and Bardram \cite{app-cop-javafwk} proposes a Java framework for COP.

Finally, the subject of context-awareness has also been addressed in work focusing on the development 
of mobile applications \cite{app-cop-mobile,app-cop-mobile2}. Here, the \emph{context} focuses more 
on concrete physical context (obtained from the device sensors) than context as an abstract 
language feature.

We approach the problem from a different perspective, building on the tradition of 
statically-typed functional programming languages and their theories.
